NumPy---Array Programming in Python

### 2020-01-11 body.tex
Add some notes

(Fig.~\ref{fig:array-proliferation})

>>>>

\fixme{NumPy is now omnipresent.  Many packages depend on it.}

- new hardware platforms; large scales of data; computational barriers; ...

\fixme{arrays are a nice idea in principle, but not all problems are that easily
solved; it breaks down when you have very large data sets, when your data
doesn't live on a single machine, when you have to use specialized hardware, or
when several resources need to be combined to solve a single array computation}

This has lead to a proliferation of arrays (Fig.~\ref{fig:array-proliferation}).
